%\setlang{USenglish}
\thispagestyle{plain}

\section*{Abstract}
Many emerging applications to be supported by upcoming 5G networks can be seen
as Networked Control Systems (NCS), i.e., feedback control loops closed over a
communication network. Delay, limited network resources, time-varying channel
conditions are common network-induced challenges which can be tackled by a
scheduler granting medium access efficiently. Age-of-Information (AoI) is a
recently introduced network metric quantifying information freshness at a
receiving network node and is meant to serve as an interface between
communication network and application. AoI has generalized joint design in NCS,
where networking policies has to consider the underlying system dynamics of its
users. It has found successful use-cases in control-aware data scheduling. In
this work, we employ AoI to calculate penalty functions used to derive an
optimal control-aware scheduling strategy. We consider multiple, heterogeneous
NCS sharing a single wireless link with time-varying channel conditions governed
by the Gilbert-Elliot model. We have implemented a channel state dependent
scheduling algorithm and obtained its complexity. However, simulations have
shown that it is not scalable due to high computational costs. Furthermore, we
have investigated possible reasons behind inconsistent behavior of our
scheduling algorithm when simulated on different operating systems. The effect
occurs on Linux, Mac and Windows and results in the scheduler distributing
network resources differently, which leads to varying performance.
